Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-19 paper/paper.tex
added info about Daedalus, started to outline operational safety

Once rebuilt and covered, we tested the \emph{Daedalus} in our shop to ensure the rebuilt structure was strong enough. Amanda and Anthony, please continue working on this paragraph, describing our testing procedures

@@

PAT

\subsection{Safety Features}

PAT

\subsection{Procedures}

PAT (well i dont know what to do here yet)

>>>>

Once rebuilt and covered, we tested the \emph{Daedalus} in our shop to ensure the rebuilt structure was strong enough. Of particular concern was interface between the wings and the center section---it was important to confirm that the wings were mounted and reinforced in a manner that would permit them to carry the load of the plane while in flight.  To this end, we put the \emph{Daedalus} through a series of static and dynamic ``sandbag tests.''  The plane was carefully supported under the center section, nose, and tail while pre-weighted bags of sand were slowly placed symetrically and simultaneously on the underside of each wing, starting from the innermost rib.  The \emph{Daedalus} easily supported XX lbs (XX percent of its weight) under static loading.  We then lifted the plane off its supports and jostled it to simulate in-flight motion.  The plane seemed to remain stable, and upon further observation after unloading, no cracks or defects were detected.

Satisfied, we proceeded through the usual engine and surface tests before taxiing the plane around a parking lot.  We brought the plane back inside, examined it for signs of stress and, finding everything in good condition, deemed the \emph{Daedalus} ready to fly.

@@

We consider the safety of our team, our aircraft, and our spectators to be of utmost importance.  As such, we've implemented numerous safety features and developed a strict procedure for starting, taxiing, and flying the plane.  This procedure enables us to ensure that all personnel are safely in place, and that no intergral checks are missed.

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby.
\begin{itemize}
\item Channel 5 (?) allows quick switch to safety pilot in case of autopilot malfunction
\item autopilot return home command if connection is lost (I presume it does something like that?)
\item kill switch
\item etc?
\end{itemize}

\subsection{Procedures}
Our team employs a clearly defined flight routine every time the engine is started.  Blah blah blah.  Maybe just include either the flight routine or pre-flight checklist as an appendix?  I feel like this stuff is pretty standard, and there's probably no point in us wasting a lot of space rambling about it.
